### 2016-07-12 R/ITHIM.Rmd
Update to MET distribution code.

```{r readnewMETs}
summaryFile <- "~/GHI/data/atussum_0311.dat"
summary <- read.table(summaryFile, header=T, skip=0, sep=",")
metaDataColumns <- 1:24
summaryList <- list(Data = summary[,-metaDataColumns], metaData = summary[,metaDataColumns])
activities <- colnames(summaryList$Data)
metKey <- newMETs$Data$AinsworthMETS
activityCode <- ifelse(nchar(newMETs$Data$X6.digit.activity.code)==5,paste0("t0",newMETs$Data$X6.digit.activity.code),paste0("t",newMETs$Data$X6.digit.activity.code))
names(metKey) <- activityCode
activities[!(activities %in% names(metKey))]
names(metKey)[!(names(metKey) %in% activities)]
```

```{r metKey}
metKeyVector <- metKey[activities]/60*7
names(metKeyVector) <- activities
metKeyMatrix <- matrix(metKeyVector, nrow = nrow(summaryList$Data), ncol = length(metKeyVector), byrow = TRUE)
METs <- rowSums(summaryList$Data * metKeyMatrix, na.rm = TRUE)
hist(METs, breaks = 75)
```

>>>>

```{r readnewMETs}
cpsFile <- "~/GHI/data/atuscps_0311.dat"
cps <- read.table(cpsFile, header=T, skip=0, sep="," )
cps <- within(cps, {
    TUCASEID <- as.character(TUCASEID)
    TULINENO <- as.character(TULINENO)
    GEREG <- as.factor(GEREG)
    })
cps <- subset(cps, TULINENO == "1")

summaryFile <- "~/GHI/data/atussum_0311.dat"
summary <- read.table(summaryFile, header=T, skip=0, sep=",")
metaDataColumns <- 1:24
summaryList <- list(Data = summary[,-metaDataColumns], metaData = summary[,metaDataColumns])

summaryList$metaData <- within(summaryList$metaData,{
    AGECAT <- ifelse(TEAGE <5, "age0-4",
                     ifelse(TEAGE > 4 & TEAGE < 15, "age5-14",
                     ifelse(TEAGE > 14 & TEAGE < 30, "age15-29",
                     ifelse(TEAGE > 29 & TEAGE < 45, "age30-44",
                     ifelse(TEAGE > 44 & TEAGE < 60, "age45-59",
                     ifelse(TEAGE > 59 & TEAGE < 70, "age60-69",
                     ifelse(TEAGE > 69 & TEAGE < 80, "age70-79", "age80+"
                            )))))))})

activities <- colnames(summaryList$Data)
metKey <- newMETs$Data$AinsworthMETS
activityCode <- ifelse(nchar(newMETs$Data$X6.digit.activity.code)==5,paste0("t0",newMETs$Data$X6.digit.activity.code),paste0("t",newMETs$Data$X6.digit.activity.code))
names(metKey) <- activityCode
rownames(newMETs$metaData) <- activityCode
```

```{r metKey}
metKeyVector <- metKey[activities]/60*7
names(metKeyVector) <- activities
metKeyMatrix <- matrix(metKeyVector, nrow = nrow(summaryList$Data), ncol = length(metKeyVector), byrow = TRUE)

METs <- data.frame(METs = rowSums(summaryList$Data * metKeyMatrix, na.rm = TRUE), AGE = summaryList$metaData$TEAGE, SEX = summaryList$metaData$TESEX, AGECAT = summaryList$metaData$AGECAT, row.names = summaryList$metaData$TUCASEID)

```{r dists}
D <- merge(cps, METs, by.y = "row.names", by.x = "TUCASEID")
ggplot(D, aes(x = METs, ..density.., colour = AGECAT)) + geom_freqpoly() + facet_grid( SEX ~ GEREG )
```

### Total Distribution

```{r total, eval = FALSE, echo = FALSE}
foo <- mapply(getTotalDistribution, muTravel = rep(37,2), cvTravel = rep(1.72,2), muNonTravel = rep(10,2), cvNonTravel = rep(1,2), p = rep(0.5,2), pWalk = rep(54.4/64.2,2), vWalk = rep(2.88,2), size = 1e4, SIMPLIFY = FALSE)
```
